Semantic Preserving Bijective Mappings for Representations of Special Functions between Computer Algebra Systems and Document Preparation Systems

### 2018-11-16 main.tex
Extend future work by mentioning Beaumont paper (close #10)

Miller also developed LaTeXML, a tool for converting \LaTeX{} expressions to MathML~\parencite{LaTeXML}. LaTeXML was used to generate the \gls*{dlmf} and is able to parse the \Macro s to content MathML. Even though many \gls*{cas} are able to import and export MathML, they fail for special functions. Schubotz et.~al recently performs benchmarks on several \LaTeX{} to MathML conversion tools, including LaTeXML, in~\parencite{DBLP:conf/jcdl/SchubotzGSMCG18}.

@@

>>>>

Miller also developed LaTeXML, a tool for converting \LaTeX{} expressions to MathML~\parencite{LaTeXML}. LaTeXML was used to generate the \gls*{dlmf} and is able to parse the \Macro s to content MathML. Even though many \gls*{cas} are able to import and export MathML, they fail for special functions. Schubotz et al.~recently performs benchmarks on several \LaTeX{} to MathML conversion tools, including LaTeXML, in~\parencite{DBLP:conf/jcdl/SchubotzGSMCG18}.

@@

A theoretical improvement for the numerical tests would be to perform the tests for specific, considered as critical, values with respect to the involved functions. J.~C.~Beamont et al.~tested  identities for multivalued elementary functions by choosing sample points from a region with respect to the branch cuts of the functions~\parencite{DBLP:journals/aaecc/BeaumontBDP07}. We assume that choosing sample points from those regions, significantly improves the results of our numerical tests.

Increasing the amount of translatable formulae in the \gls*{dlmf} and improving the verificiation techniques are parts of ongoing projects.
